### 2022-05-15 README.Rmd
Test plot
modify readme

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("xuan-liang/ggmatplot")
```

@@

If two matrices with equal number of columns are used, the corresponding columns of the matrices will be plotted against each other. i.e. column 1 of matrix `x` will be plotted against column 1 of matrix `y`, column 2 of matrix `x` will be plotted against column 2 of matrix `y`, etc.

The next example uses the iris dataset, with matrices `x` and `y` as shown below. The `Sepal.Length` is plotted against `Sepal.Width` and the `Petal.Length` is plotted against `Petal.Width`. Therefore the groups 'Column 1' and 'Column 2' can be interpreted as 'Sepal' and 'Petal' respectively. To make the plot more meaningful, we can further add the legend label and axis names by `legend_label`, `xlab` and `ylab`.

@@

Next is plot of the US personal expenditure over 5 categories and 5 years, and is a simple example of how wide format data can be used with `ggmatplot()`. Note how the expenditure categories to be used on the x axis is used as vector `x`, and the expenditure values is used in wide format as matrix `y` - with its columns corresponding to the grouping structure.

The plot specifies the plot type as `plot_type = "both"`, which is a combination of 'point' and 'line' plots. It customized using `ggmatplot()` parameters and a `ggplot` theme as well.

@@

Boxplots accept only a single matrix or data frame as well, and uses its columns as individual groups. While `ggmatplot` plots are filled by default, the fill color can be made transparent by using `alpha = 0`.

@@

ggmatplot(x,
  plot_type = "boxplot",
  alpha = 0, # removing fill values
  xlab = "", ylab = ""
)
```

Violin plots too accepts a single matrix or data frame input, and behaves similar to density plots and boxplots.

@@

Dotplots too accept a single matrix input and plots the distribution of each of its columns.

The next example uses the `plot_type = "dotplot"` to visualize the distribution of the data, and also customizes the position of the legend using a `ggplot` theme as well.

@@

ggmatplot(x,
  plot_type = "dotplot",
  color = c("#00AFBB", "#E7B800"),
  xlab = "", ylab = ""
) +
  theme(legend.position = "bottom")
```

Similar to density, violin, dotplots, and box plots, histograms too accept a single matrix or data frame input and groups the plot using its columns. The histogram in the following example uses a matrix of 4 columns, and therefore groups the plots based on these 4 columns. The plot is also faceted by group.

@@

ggmatplot(x,
  plot_type = "histogram",
  xlab = "Group",
  color = "black",
  fill = c("#F8766D", "#7CAE00", "#00BFC4", "#C77CFF")
) +
  facet_wrap(~Group, scales = "free")
```

@@

ggmatplot(x,
  plot_type = "ecdf",
  xlab = "Group",
  size = 1
) +
  theme_minimal()
```

@@

The next example construct out an `errorplot` using the medians and interquartile ranges of each variable.

@@

ggmatplot(x,
  plot_type = "errorplot",
  desc_stat = "median_iqr",
  xlab = "Group",
  size = 1
) +
  theme_minimal()
```

>>>>

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("xuan-liang/ggmatplot")
```

@@

If two matrices with equal number of columns are used, the corresponding columns of the matrices will be plotted against each other, i.e. column 1 of matrix `y` will be plotted against column 1 of matrix `x`, column 2 of matrix `y` will be plotted against column 2 of matrix `x`, etc.

The next example uses the iris dataset, with matrices `x` and `y` as shown below. The `Sepal.Width` is plotted against `Sepal.Length` and the `Petal.Width` is plotted against `Petal.Length`. Therefore the groups 'Column 1' and 'Column 2' can be interpreted as 'Sepal' and 'Petal' respectively. To make the plot more meaningful, we can further modify the legend label and axis names by `legend_label`, `xlab` and `ylab`.

@@

Next is the plot of the US personal expenditure over 5 categories and 5 years, and is a simple example of how wide format data can be used with `ggmatplot()`. Note how the expenditure categories to be used on the x axis is used as vector `x`, and the expenditure values is used in wide format as matrix `y` - with its columns corresponding to the grouping structure.

The plot specifies the plot type as `plot_type = "both"`, which is a combination of 'point' and 'line' plots. It is further customized by using `ggmatplot()` parameters and a `ggplot` theme as well.

@@

Boxplots accept only a single matrix or data frame as well, and uses its columns as individual groups. By default, the fill color is white. But it is easy to customize and the transparency can be modified by the `alpha` parameter.

@@

ggmatplot(x,
  plot_type = "boxplot",
  color = 'black', 
  fill = 'grey',
  alpha = 0.8,
  xlab = "", ylab = ""
)
```

Violin plots accept a single matrix or data frame input, and behave similar to density plots and boxplots.

@@

Dotplots too accept a single matrix input and plot the distribution of each of its columns. The next example uses the `plot_type = "dotplot"` to visualize the distribution of the data with the custom color and binwidth value. Note that the default setting for binwidth is 1/30 of the range of the data.

@@

ggmatplot(x,
  plot_type = "dotplot",
  color = c("#00AFBB", "#E7B800"),
  binwidth = 0.1,
  xlab = "", ylab = ""
)
```

Similar to density, violin, dotplots, and box plots, histograms too accept a single matrix or data frame input and group the plot using its columns. The histogram in the following example uses a matrix of 4 columns, and therefore groups the plots based on these 4 columns. The plot is also faceted by group and the legend is removed by a `ggplot` theme setting.

@@

ggmatplot(x,
  plot_type = "histogram",
  xlab = "",
  color = "black",
  fill = c("#F8766D", "#7CAE00", "#00BFC4", "#C77CFF")
) +
  facet_wrap(~Group, scales = "free") + 
  theme(legend.position = 'none')
```

@@

ggmatplot(x,
  plot_type = "ecdf",
  xlab = "",
  ylab = 'Empirical CDF',
  size = 1
) +
  theme_minimal()
```

@@

The next example, plots out an `errorplot` using the medians and interquartile ranges of each variable.

@@

ggmatplot(x,
  plot_type = "errorplot",
  desc_stat = "median_iqr",
  xlab = "",
  size = 1
) +
  theme_minimal()
```
